\documentclass[12pt, letterpaper, twoside]{article}
\usepackage[utf8]{inputenc}

\title{Rocks and Minerals: Everyday Uses}
\author{Francisco Javier Guijarro \thanks{funded by IES JC1}}
\date{October 2021}

\begin{document}
\maketitle
We use things made from rocks and minerals every day. The items in this case are just a few of the ways that we use rocks and minerals in our everyday lives.

\section{Gypsum, chalk and slate}
	\begin{itemize}
		\item \textbf{Gypsum} is the basis for \textbf{drywall}.
		\item \textbf{Chalkboards} are made from \textbf{slate}.
		\item \textbf{Chalk} is a limestone made of the skeletons of millions of microbes.
	\end{itemize}
	
\section{Clay Mudstone}
\textbf{Ceramics} are made from clay mudstone.

\section{Granite, Salt, Quartz and Marble}
	\begin{itemize}
		\item \textbf{Granite} and \textbf{marble} counter tops are made from stone.
		\item \textbf{Salt} is and essential nutrient.
		\item \textbf{Glass} is formed by melting \textbf{quartz}.
	\end{itemize}
	

\section{Sulfur and Flint}
	\begin{itemize}
		\item \textbf{Sulfur} is an integral part of gunpowder and matches
		\item \textbf{Flint} is a form of quartz.
	\end{itemize}

\section{Garnet and Talc}
	\begin{itemize}
		\item \textbf{Garnet} is a gemstone used as \textbf{abrasive} for both sand blasting and sand paper.
		\item \textbf {Talc} is used in \textbf{baby powder}.
	\end{itemize}
	
\section{Pumice and Obsidian}
	\begin{itemize}
		\item \textbf{Obsidian} is a extremely hard rock used for \textbf{surgical scalpels}
		\item \textbf{Pumice} is used as and \textbf{abrasive}
	\end{itemize}
	
\section{Copper and Zinc}
	\begin{itemize}
		\item \textbf{Copper} has low resistance to electrical charge and is abundant, so it is used for \textbf{wiring}
		\item \textbf{Zinc} is and essential element and can be taking as a supplement. It is also used for \textbf{galvanizing} to prevent coating.
	\end{itemize}









\end{document}